% Write a <300 word biography
% http://www.gradhacker.org/2011/09/23/narrating-your-professional-life-writing-the-academic-bio/

Daniel Bosk is a doctoral student at KTH Royal Institute of Technology, 
Stockholm, Sweden, and a lecturer of Computer Engineering at Mid Sweden 
University, Sundsvall, Sweden.
He holds a Master of Science in Computer Science from KTH Royal Institute of 
Technology and a Master of Education in Mathematics and Computer Science from 
Stockholm University, Sweden.
His research interests are in security and privacy in decentralized systems, 
and specifically the empowerment of the users.

Guillermo Rodr\'{\i}guez-Cano is a doctoral student at KTH Royal Institute of 
Technology, Stockholm, Sweden.
He holds a Master of Science in Computer Science from Uppsala University, 
Sweden, and a Bachelor of Engineering in Computer Science from University of 
Valladolid, Spain.
His research interests lie in the area of privacy and security in social 
systems, privacy-preserving data mining, and information propagation in 
social networks.

Benjamin Greschbach defended his Ph.D.\ thesis on Privacy Issues in Decentralized 
Online Social Networks and other Decentralized Systems at KTH Royal Institute 
of Technology, Stockholm, Sweden in December 2016. During his Ph.D.\ studies he 
co-authored eleven articles in the fields of Computer Security and Privacy. 
Before, he studied Computer Science at the University of Freiburg, Germany 
with one year visit at Chalmers University in Gothenburg, Sweden.

Sonja Buchegger is an associate professor of Computer Science at KTH Royal 
Institute of Technology, Stockholm, Sweden.
Prior to KTH, she was a
senior research scientist at Deutsche Telekom Laboratories in Berlin, Germany,
a post-doctoral scholar at the University of California at Berkeley, USA, 
and a researcher at the IBM Zurich Research Laboratory, Switzerland.
Her Ph.D.\ is in Communication Systems from EPFL, Lausanne, Switzerland, and 
she graduated in Computer Science from the University of Klagenfurt, Austria.
Her main research interests are in privacy and decentralized systems.
