So far we have treated only one-to-one conversations, i.e.\ Alice and Bob 
talking to each other.
However, there are usually more than two people organizing a protest, and so we 
need to hold discussions with more than only two people at a time.
In this situation there are two approaches to solving the communication:
simultaneous pair-wise communication between all participants or true group 
communication.
Furthermore, how the messages are distributed is also important, because Eve 
can learn who the participants are.

\subsubsection{Group Communication Properties}
\label{GroupProperties}

When a group uses pair-wise communication, every member of the group will set 
up a pair-wise channel to each other member of the group.
Each pair-wise channel is as described above, in \cref{Communicating}.
Then for every message Alice wants to send to the group she has to send it to 
every participant.
This would allow Alice to cheat, e.g.\ she can send \enquote{Who wants to 
  overthrow the regime?} to everyone except to Bob, to whom she instead sends 
\enquote{Who wants to order pizza?}.
This opens up for the Byzantine Generals' problem~\cite{ByzantineGenerals}, 
where malicious actors can lie to honest actors to disrupt operation.
\citet{ByzantineGenerals} in fact proved that it is impossible for the honest 
parties to recover and identify the malicious parties if the malicious parties 
exceed a third of the participants.
  
Although Alice's ability to say different things to different participants is 
in itself a desirable property from Alice's perspective --- she would like to 
lie to suspected regime agents --- this property can at the same time be 
undesirable due to the Byzantine Generals' problem.
For this reason group communication must provide better properties, namely that 
everyone hears who said what and when, thus forcing Alice to say the same thing 
to all participants.
In such a scheme, when Bob replies \enquote{I do, shall we say tonight?} the 
others will see that Bob is replying to something they did not see and not to 
the question \enquote{Who wants to overthrow the regime?}.

\citet{multiotr2009} tried to extend the \ac{OTR} protocol to a multi-party 
setting.
This did not result in a concrete protocol implementation, and the resulting 
protocol they suggested was also very complex.
It also had some undesirable limitations, for instance, the scenario that Bob 
receives a question which is different from everyone else's is only detected at 
the very end of the conversation.
As is pointed out by \citet{TSgroups}, asynchronous communication today has no 
real end, which makes the approach of \citet{multiotr2009} even less appealing.
Due to this, \citet{SignalApp} implements group chats as simple pair-wise 
conversations.
With additional meta-data they can ensure consistent history, however, this is 
not yet implemented~\cite{TSgroups}.
A technique that could be used for this is to include a message digest of the 
entire conversation history with each message.
A message digest is computed using a one-way function, i.e.\ its output is 
unpredictable and its input is impossible to compute given only the
output. %TODO: explain more clearly
This means that the message digest included in Bob's reply and the one computed 
by the other participants above would differ, thus everyone learns that the 
conversation history is inconsistent and should no longer be trusted.
Due to the unpredictable property of the one-way function, Alice cannot phrase 
the two different messages in such a way that they yield the same message 
digest in the history either.
But despite this, the other participants cannot determine if it is Alice or Bob
who is lying about the message history --- Alice could send the same message to
everyone and still Bob could try to frame her.

\subsubsection{Message Distribution}
\label{MessageDistribution}

\input{DecentAC.tex}

