\section{During a Protest}
\label{DuringProtest}

There are a few aspects that we must cover which relate to this part of our 
treatment.
During a protest, organizers and demonstrators might want to communicate, 
either among themselves or to the outside world.
The communication to the outside world can have at least two purposes.
The first one is simply to try to get more people to come to the demonstration.
The second is when a demonstrator wants to store something for posterity.
This can be a photo capturing police brutality or a part of 
a proof-of-demonstration (as in \cref{AfterProtest}).

There are a few problems with communication during a protest.
If the participants use the phone network, i.e.\ infrastructure which is 
generally controlled by the government, participants can be tracked and bound 
to the location by their phone.
If they communicate over the phone network they can still use the techniques 
outlined in \cref{BeforeProtest}.
However, if they do not want to be tracked, there are two options:
\begin{enumerate}
  \item they must use another network infrastructure that is not controlled by 
    the government,
  \item the mechanisms in \cref{BeforeProtest,AfterProtest} must allow 
    executions without access to a global communications infrastructure during 
    the demonstration.
\end{enumerate}

There are solutions to the first problem: wireless ad-hoc networks.
The area of ad-hoc networks is far too wide for us to convey more than the 
general idea of the field in this chapter.
\input{AdhocNetworks.tex}

For the second problem listed above, we can achieve local communication, e.g.\ 
pair-wise communication through bluetooth or \ac{NFC}.
So we can assume that this possibility exists.
However, communicating certain data to the outside world will still be the 
ultimate goal, but we will use the local communication possibilities to ensure 
the authenticity of the data after the demonstration is over.
We will discuss this further in \cref{AfterProtest}.

