\section{Introduction}
\label{Introduction}
The rapid development of information and communication technology (ICT) in the latter half of the
20th century and its increasing prevalence in
everyday life has helped a considerable part of the world to reach the
21st century with a means of having real-time secure
communications.  These developments, however,  have come
with some side effects, for example in data collection. Better storage
technologies have allowed for longer data retention policies for both
the private and public sectors, not only providing new and better
services to users, or means to combat crime, but also compromising the privacy of
citizens, and sometimes their safety in oppressive regimes.

Among these technological advances, \acp{OSN} (in the broadest sense,
any kind of online social media) stand out as a popular
computer-mediated tool allowing people and other entities to interact
by sharing and exchanging information of any kind. Computation power
and network communication are combined to make social interactions
between people possible at any time and place, lowering
political, economical and geographical boundaries. Such social media
are increasingly used for political activism ranging from showing
one's leanings by liking something to actual support and organization
of protests.

Many \acp{OSN} are run in a centralized manner --- the service
provider acts as a communication channel between the users of the
\ac{OSN}. Such a structure allows providers to oversee a large portion
of the data, if not all, exchanged between the users. Bearing in mind
that in the case of \acp{OSN}, much of it is of personal and sensitive
kind, for example, posting a picture in the network may reveal the
physical geolocation of the poster as this information can be embedded
in the meta-data of the image or even inferred by image processing for
place recognition. This has proved to be problematic for political
activism in several ways: a centralized ownership and control make it
easier to shut down, for example, the governmental block of Twitter in
Turkey for several days~\cite{TurkeyBansTwitter}, or public
institutions can subpoena (at best) or just seize information from the
service provider. Moreover, the massive collection of data in these
networks makes them an ideal target for attackers such as competing
service providers or even governmental agencies. For example, in
recent years, intelligence and security agencies of some countries
have targeted these services to gain personal information about their
citizens, enemies and even allies~\cite{Prism}. Since a centralized
system can log not only data the users upload but also
meta-information about their behaviour, such as online times, whom
they communicate with, their location and social ties, there is a
wealth of information to connect a person to a cause.

While we acknowledge the benefits of such technological advances like
\acp{OSN}, we also point out the costs to personal privacy and
advocate for the need to develop \acp{PET} that can co-exist with
these technologies. A prominent example is Tor~\cite{Tor}, a routing
mechanism for online anonymity and censorship
resistance. Decentralized solutions try to achieve provider
independence and, in some cases, also offer censorship
resistance. Privacy-preserving technologies aim at providing data
protection by prevention, i.e., making privacy breeches and data leaks
technically impossible. For example, by means of cryptographic
techniques, an organization could enforce certain policies (say,
access control by cryptographic means) instead of relying on
compliance by insiders and on the security of the system and its
maintenance to protect from
intrusions. %TODO: good example with reference; almost done

Besides providing technological support to the conventional and
long-established form of protesting physically, online technologies
have also opened the possibility to alternative ways, such as virtual
\enquote{petitions}, or in general, expressing support for an opinion
in the form of an encouraging comment or simply affirmation.

In this chapter we focus on describing some privacy-enhancing tools in
the context of \acp{OSN} that we believe can be useful in a protest
and that have not yet seen a widespread use in practice. Although a
protest itself relies mainly on the traditional physical act of
gathering, we believe that it would benefit from some of the
developments originated in the fields of information security and
privacy.

\subsection{The Protesting Scenario}

The topic of protesting is rather wide.
As suggested above, it could take the form of showing support for a statement 
in \iac{OSN}.
It could also take the form of people joining together in the streets for 
a demonstration.
For this chapter we will consider the following scenario:
Alice\footnote{%
  We use the nomenclature of the Computer Security field,
  where one user of the system (usually called Alice) tries to securely communicate
  with another (usually called Bob) and others (the so-called adversaries, usually
  named Eve) are trying to interfere, eavesdrop or otherwise attack the
  system. 

} lives in a country under the rule of an authoritarian regime.
Alice wants to organize the opposition and lead a public demonstration to show 
that the people want a democratically reformed government.
As expected, the authoritarian regime wants to prevent this from happening.
The regime's goal is to oppress the opposition so that they cannot ever reach 
a big-enough demonstration to show the majority's dissatisfaction.
They have assigned Eve who will try to stop Alice as early as possible to avoid 
that her ideas spread throughout the population.

Although our scenario is set in an authoritarian regime, privacy
preservation is needed also in ostensible democracies, as illustrated
by whistle-blowers such as Edward Snowden. 
%, the tools and techniques described below are also useful in other systems of
%governance, such as democracies.  
A technical solution can potentially prevent privacy breaches and be
used to enforce data protection mandated by law as well as offer
additional privacy protection where such protection is insufficient.

\input{terrorists.tex}

\subsection{Scope and Outline}
\label{Outline}

Over the years, we have developed privacy-preserving building blocks
for \acp{DOSN}.  In this chapter we will describe how some of these
can benefit the activist Alice in the scenario given above and
complement with works from others\footnote{We describe both ours and
  works by others in the third person as the focus should be on the
  research itself.}. Much of this is still in the realm of research
and hence comes with the caveat that it is not tested in the field or
in some cases even implemented beyond a
proof-of-concept. Nevertheless, this research represents examples of
possible technologies within reach for activist support in the near
future and a step toward reaching across communities to open a dialog.

In the rest of the chapter, we describe these privacy-enhancing tools
in relation to how they can be used; more specifically, we categorize
them as applicable before, during or after a protest. The first part,
\cref{BeforeProtest}, is about organization, coordination, and
communication needed to prepare a protest.  Then we briefly discuss
the protection of communication between activists or to outsiders (for example, the
press) during the protest, even in the case when the public network
infrastructure cannot be trusted, in \cref{DuringProtest}.
    Finally, we talk about following up a protest by the organizers, not only to assess their success 
    but also to correct the flaws for the next time.  For example, the 
    organizers may want to obtain reliable statistics on the number of 
    attendees per area, but protect that data from unauthorized
    entities, for example the police.
    We discuss different authenticity and verifiability properties of use for 
    this stage in \cref{AfterProtest}.


Before starting, however, we must provide a short discussion of some technical 
limitations.
