\section{Before a Protest}
\label{BeforeProtest}

Alice is an activist in an authoritarian regime and she want to organize 
a demonstration.
This means that the regime wants to stop Alice while she prepares the 
demonstration.
Consequently, Alice wants to do all preparations in such a way that she 
minimizes the risk of interference.
In this section we will focus on two aspects: the communication between the 
activists and their agreement on the details of the demonstration event.

\paragraph{Communication.}

Alice and her co-organizers must communicate with each other.
A trivial solution to the communication problem is the traditional face-to-face 
meeting --- with the trade-off that the invited attendants should be able to 
meet at the same time in the same place.
This is not always easy to achieve, so Alice wants to complement this by 
electronic communications.
Thus Alice wants to communicate with Bob by means of a secure channel to 
prevent the regime's agents from eavesdropping on their conversations.

Secure communication can be divided into two problems: bootstrapping and the 
actual communication.
There are several tools that we will discuss related to this.
In \cref{UserSearch}, we will discuss how Alice and Bob can find each other in 
\iac{DOSN}, this relates to the bootstrapping problem.
Then we discuss security and privacy properties of the communication problem, 
we focus on one-to-one secure communications in \cref{Communicating}.
There is also the case where Alice wants to talk to more people than just Bob, 
and this case is discussed in \cref{Discussions}.

\paragraph{Agreement.}

Alice and the co-organizers must agree on a time and place to hold the 
demonstration.
This can also be extended to including interested participants.
For example, the organizers might be interested in estimating how many invited 
participants are really committed to attend the event, but in such a way that 
they do not reveal the details --- which the regime can use to thwart it --- 
such as the location and any identities.
At the same time, the participants who have committed to attend may want to 
have assurances that they will be told the details of the protest if they 
express their commitment to the organizers.
We discuss some aspects of this problem in \cref{InvitingParticipants}.


% Searching for your friends
\input{UserSearch.tex}

% Communication between people
\input{PairwiseComm.tex}

% Holding discussions
\input{discussions.tex}

% Inviting participants
\input{EventInvitations.tex}

% Having a Decentralized Account
%\input{passwd.tex}
