\subsection{Holding Discussions}
\label{Discussions}

So far we have treated only one-to-one conversations, i.e.\ Alice and Bob 
talking to each other.
However, there are usually more than two people organizing a protest, and so we 
need to hold discussions with more than only two people at a time.
In this situation there are two approaches to solving the communication:
simultaneous pairwise (one-to-one) communication between all participants or 
multicast communication.
Furthermore, how the messages are distributed is also important, because Eve 
might be able to learn who the participants are.

\subsubsection{Group Communication}
\label{GroupCommunication}

When a group uses pairwise communication, every member of the group will set up 
a one-to-one channel to each other member of the group.
Each pairwise channel is as described above (\cref{Communicating}).
Then for every message Alice wants to send to the group she has to send it to 
every member.
This would allow Alice to cheat, e.g.\ she can send \enquote{Who wants to 
  overthrow the regime?} to everyone except to Bob, to whom she instead sends 
\enquote{Who wants to order pizza?}.
This opens up for the Byzantine Generals' problem~\cite{ByzantineGenerals}, 
where malicious actors can lie to honest actors to disrupt operation.
\textcite{ByzantineGenerals} in fact proved that it is impossible for the 
honest parties to recover from this and identify the malicious parties if the 
malicious parties exceed a third of the participants.
  
Although Alice's ability to say different things to different participants is 
in itself a desirable property from Alice's perspective --- she would like to 
lie to suspected regime agents --- this property can at the same time be 
undesirable due to the Byzantine Generals' problem.
For this reason group communication must provide better properties, namely that 
everyone hears who said what and when, thus forcing Alice to say the same thing 
to all participants.
In such a scheme, when Bob replies \enquote{I do, shall we say tonight?} the 
others will see that Bob is replying to something they did not see and not to 
the question \enquote{Who wants to overthrow the regime?}.

%\textcite{multiotr2009} tried to extend the \ac{OTR} protocol to a multi-party 
%setting.
%This did not result in a concrete protocol implementation, and the resulting 
%protocol they suggested was also very complex.
%It also had some undesirable limitations, for instance, the scenario that Bob 
%receives a question which is different from everyone else's is only detected at 
%the very end of the conversation.
%As is pointed out by \textcite{TSgroups}, asynchronous communication today has 
%no real end, which makes the approach of \citeauthor{multiotr2009} even less 
%appealing.
%Due to this,
\textcite{SignalApp} implements group chats as simple pairwise conversations.
With additional meta-data they can ensure consistent history~\cite{TSgroups}.
A technique that could be used for this is to include a message 
digest\footnote{%
  A message digest is computed using a cryptographic hash function, i.e.\ 
  a one-way function.
  The output of such functions is unpredictable, e.g.\ finding two inputs that 
  yield the same output is \enquote{impossible}.
  It is also \enquote{impossible} to infer its input from its output.
  By \enquote{impossible} we mean that the probability of success is close to 
  \(\sfrac{1}{\sqrt{2^n}}\), where \(n\) usually is at least \(256\).
} of the entire conversation history with each message.
If Alice would cheat Bob as above, this means that the message digest included 
in Bob's reply and the one computed by the other participants above would 
differ, thus everyone learns that the conversation history is inconsistent and 
should no longer be trusted.
Due to the unpredictable property of the message digest, Alice cannot phrase 
the two different messages in such a way that they yield the same message 
digest in the history either.
But despite this, the other participants cannot determine if it is Alice or Bob
who is lying about the message history --- Alice could send the same message to
everyone and still Bob could try to frame her.

\subsubsection{Message Distribution}
\label{MessageDistribution}

\input{DecentAC.tex}

