\subsection{Communication between People}
\label{Communicating}

We will now focus on communication between pairs of people, e.g.\ Alice talking 
to Bob.
\citeauthor{otr2004} designed a secure protocol for two-people communication, 
the \ac{OTR} protocol.
This protocol was used as the base and has now been replaced by the Signal 
protocol\footnote{%
  The protocol used in popular messaging apps such as Signal and WhatsApp.
}.
\citeauthor{otr2004} desired an electronic equivalent of face-to-face 
conversations, i.e.\ a protocol which yield no binding proofs:
if Alice and Bob have had a conversation, Bob cannot prove anything to Eve 
about what Alice has said --- the same as in a face-to-face conversation.
This property is not true for email or most centralized communication
services. In the following, we discuss the limitations of these
traditional means of communication and the advancements in terms of
security and privacy of newer approaches.

\subsubsection{Email and Centralized Services}

The standard email system does not provide any confidentiality or 
integrity.
A suitable analogy would be that of a postcard.
Alice writes her message to Bob on a postcard without any envelope, i.e.\ her 
message and Bob's address are visible on it\footnote{%
  She must write her full return address on it too.
}.
This means that the postman can read everything.
Furthermore, most postmen use transparent sacks\footnote{%
  Some postmen have started using non-transparent sacks, so those postcards can 
  only be read by the staff in the post-office.
} to carry the postcards, so everyone along the way can also read the sender's 
and recipient's address and the contents.
This means that Eve can read the contents of these messages too.

Thus the email system provides no confidentiality: both the server used for 
sending and the server used for receiving and storing the email can read the 
contents in plain text.
If these servers do not use an encrypted connection, which is not mandatory, 
each network operator along the route can also read (and make a copy of) each 
email --- in plain text.
In 2013, \textcite{Fibretap} published that \ac{GCHQ} did exactly this on 
a worldwide scale.
Clearly, this is undesirable for Alice and Bob, since Eve can do exactly this 
too.

It is actually worse than that: the email system provides no integrity either.
This means that the postman, or Eve\footnote{%
  Or any network operator along the way.
}, can do arbitrary modifications to the messages without anyone noticing the 
difference.
This means that Eve can modify Alice's messages to Bob and Bob will not notice.

When using a centralized communications service, such as Facebook, the
level of security and privacy we can achieve is that the postman
carries non-transparent sacks.  The business model of most such
services is to read people's postcards to better profile their
interests and thus deliver better suiting advertising.
In this case, Eve can cannot directly see who is communicating with whom.
She can only see that something goes to and from the service.
However, all information is available
internally to the service.  This means that there are ways of learning
this.
One approach was illustrated by \acg{NSA} PRISM programme~\cite{Prism}, where 
the \ac{NSA} could systematically fetch user data from the major centralized 
services (Facebook, Google, Microsoft and Yahoo among others) and could query 
this data at their own discretion.
This might not work for governments like China, since these services are 
located outside China.
But because they are centralized, they are easy to censor.
This in turn forces Alice and Bob to use services which are located in China where this 
type of attack is again possible.

\subsubsection{Secure Email and Text Messaging}

Alice and Bob can add a layer of confidentiality and integrity on top of any 
insecure communication system.
Secure email works by employing cryptography: Alice encrypts the contents of 
the postcard (confidentiality) and then adds a digital signature to prevent 
modifications (integrity).
This requires that Alice and Bob verify each others keys before any 
communication --- to avoid being tricked by Eve.
Now Bob is the only one who can read Alice's message and he can also verify 
that the message is indeed from Alice and has not been modified along the way.

%To make key management easy, most schemes use public-key cryptography.
%This means that we have two keys, one which is public and another which is kept
%private.
%For encryption, the public key can transform a message to a ciphertext, i.e.\ 
%a random-looking text string.
%The private key can be used to transform the ciphertext back to the message.
%Given only the public key, it is \enquote{impossible} to find the private key.
%For signatures, we can use the private key to compute a signature of a message 
%and then send the message and its signature.
%The recipient can then use the public key to verify the signature of the 
%message.
%This signature depends on the entire message, so it is impossible to move 
%a signature to another message --- unlike signatures on paper.
%And since it is impossible to find the private key given only the public key, 
%no one can create fake signatures.

One problem with this approach to secure email is that the sender and recipient
are still in the clear, anyone can read them.
The content is hidden, but the meta-data is not.
This allows Eve to infer the social graph, by monitoring who is communicating 
with whom.

Another problem is that the digital signatures provide a property called 
non-repudiation.
Say that Alice securely sent an email to Bob, if Eve would compromise Bob's 
private key, as many government agencies can, then she would learn that Alice 
--- and no one else --- has sent that message to Bob.
Bob might even give the message and his key to Eve voluntarily or under threat.
This is exactly the property that \citeauthor{otr2004} wanted to remove with 
\ac{OTR}.
They do this by using the interactive nature of \ac{IM} and changing the 
digital signatures to shared-key \acp{MAC}.
Shared-key means that Alice and Bob share the same key\footnote{%
  Unlike with digital signatures, where Alice has a public and a private key.
  She creates signatures using her private key and Bob can verify these 
  signatures using her public key.
} for generating and verifying \iac{MAC}.
This means that Bob can generate a valid \ac{MAC} for any message and show to 
Eve, thus he cannot prove to Eve what Alice has said --- since he could have 
created this \enquote{proof} himself.
However, in this situation, Eve still has only two candidates as the author of 
the message: Alice and Bob, since they both have access to the shared keys.
%In addition, Alice and Bob do not use the same \ac{MAC} key throughout their 
%conversation, they continuously exchange new keys, one for each message.
To remedy this problem Alice and Bob uses a new \ac{MAC} key for each message.
When a message has been confirmed as received they publish the \ac{MAC} key for 
that message, i.e.\ when they no longer need them.
This gives \enquote{everyone} the possibility of generating messages that 
verifies under Alice and Bob's key, so now Alice and Bob can argue that someone 
else (Eve included) could have modified the ciphertext.
(We will return to this in \cref{WhenAdversaryControlsNetwork}.)

\textcite{SignalApp} (formerly TextSecure) improved some properties of \ac{OTR} 
in the Signal protocol, which has been formally analysed by 
\textcite{TextSecureAnalysis,SignalProtocolAnalysis}.
The main change from \ac{OTR} is that Signal uses deniable authentication.
In Signal the authentication is set up in such a way that any person knowing 
the public keys of Alice and Bob can generate a fake transcript of 
a conversation.
The result is that Eve has many more candidates for the authorship of 
a conversation.

\input{OTPKX.tex}
